Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A Tutorial Using the Bayes Factor via the Encompassing Prior Approach

### 2022-10-15 Documents/Paper/paper.Rnw
add paper preprint

Data used for the illustrative application are part of a larger project on the social-emotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]). All materials and data are available at \url{https://doi.org/10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.

@@

#----    load drake    ----

@@

All analyses were conducted using R statistical software \parencite[Version \Sexpr{paste(version$major,version$minor, sep = ".")};][]{rcoreteamLanguageEnvironmentStatistical2021}. All materials, data, and analysis code are available at \url{https://doi.org/10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}. Supplemental Material with further details is also available online at \url{https://claudiozandonella.github.io/Attachment/}.

@@

>>>>

All materials and data are available at \url{https://doi.org/10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}. Online supplemental material available via GitHub Pages at \url{https://claudiozandonella.github.io/Attachment/}.

@@

#----    load targets    ----

@@

All analyses were conducted using R statistical software \parencite[Version \Sexpr{paste(version$major,version$minor, sep = ".")};][]{rcoreteamLanguageEnvironmentStatistical2021}. All materials, data, and analysis code are available at \url{https://doi.org/10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}. Supplemental Material with further details is also available online via GitHub Pages at \url{https://claudiozandonella.github.io/Attachment/}.

Note that data used for the illustrative application are part of a larger project on the social-emotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section*{Author Contributions}

Conceptualization: C. Zandonella Callegher, T. Marci, P. De Carli, and G. Altoè;
Methodology: C. Zandonella Callegher, T. Marci, P. De Carli, and G. Altoè;
Software: C. Zandonella Callegher and G. Altoè;
Formal Analysis: C. Zandonella Callegher and G. Altoè;
Investigation: T. Marci and  P. De Carli;
Data Curation: T. Marci and C. Zandonella Callegher;
Writing – Original Draft: C. Zandonella Callegher;
Writing – Review \& Editing: T. Marci, P. De Carli, and G. Altoè;
Visualization: C. Zandonella Callegher;
Supervision: G. Altoè;
Project Administration: G. Altoè;

\section*{Conflicts of Interest}

The authors declare that there were no conflicts of interest with respect to the authorship or the publication of this article.

\section*{Supplemental Material}

All materials and data are available at \url{https://doi.org/10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}. Online supplemental material available via GitHub Pages at \url{https://claudiozandonella.github.io/Attachment/}.

Note that data used for the illustrative application are part of a larger project on the social-emotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]).

% \section*{Prior versions}
%
% Preprint version of the submitted manuscript is available at [TODO].
